ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
authors things

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Guarracino, Heumos \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

    \corresp{$^\ast$To whom correspondence should be addressed.}

@@

    \abstract{
        \textbf{Motivation:} Pangenome graphs provide a complete representation of
        genomic information that allows for complex population-sized analysis of genomes
        without introducing reference genome bias.
        %
        \\
        \textbf{Results:} Here we present \odgi\, a novel range of tools that makes use of an efficient
        in-memory representation of DNA graphs structured in the variation graph model. \odgi\ can
        handle hundreds of large genomes while maintaining fast execution runtime and low memory overhead.
        \odgi\ includes tools for detecting complex regions, extracting \textit{loci}, exploratory analysis,
        sorting, removing artifacts, and graphs manipulation and visualisation.
        %
        \\
        \textbf{Availability:} \odgi\ is software written in the \Cpp\ programming language and
        published under the libre MIT license. Source code and user manual can be downloaded from
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        %
        \textbf{Contact:}
        \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        \href{erik.garrison@gmail.com}{erik.garrison@gmail.com}\\
        \\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.}

>>>>

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Guarracino, Heumos \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}\dagger,*}$,
        Simon Heumos\,$^{\text{\sfb 2,}\dagger}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Biology, University of Tor Vergata, Rome, 00133, Italy \\
        $^{\text{\sf 2}}$QBiC, University of Tübingen, Tübingen, XXXXXXXXXX, Germany \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

    \corresp{$^\ast$To whom correspondence should be addressed.}
    \corresp{$^\dagger$Shared first authorship.}

@@

    \abstract{
        \textbf{Motivation:} Pangenome graphs provide a complete representation of
        genomic information that allows for complex population-sized analysis of genomes
        without introducing reference genome bias.
        %
        \\
        \textbf{Results:} Here we present \odgi\, a novel range of tools that makes use of an efficient
        in-memory representation of DNA graphs structured in the variation graph model. \odgi\ can
        handle hundreds of large genomes while maintaining fast execution runtime and low memory overhead.
        \odgi\ includes tools for detecting complex regions, extracting \textit{loci}, exploratory analysis,
        sorting, removing artifacts, and graphs manipulation and visualisation.
        %
        \\
        \textbf{Availability:} \odgi\ is software written in the \Cpp\ programming language and
        published under the libre MIT license. Source code and user manual can be downloaded from
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        %
        \textbf{Contact:}
        \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        \href{erik.garrison@gmail.com}{erik.garrison@gmail.com}\\
        \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.}
